Exp 2 of 4

### 2016-08-13 experiments/e2/writeup/e2-b-knitr.tex
tidying up

\documentclass[a4paper,12pt]{article}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

@@

\usepackage{alltt}
\usepackage[margin=2cm]{geometry}
\usepackage{placeins}

\title{Exp 2 of 4}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

@@

@@

@@

@@

{\centering \includegraphics[width=\maxwidth]{figure/graphics-plotMainsa-1}

@@

\caption[Plot main effects on several transformations]{Plot main effects on several transformations}\label{fig:plotMainsa}
\end{figure}

@@

{\centering \includegraphics[width=\maxwidth]{figure/graphics-mainB-1}

@@

\caption[Just the main effects]{Just the main effects}\label{fig:mainB}
\end{figure}

@@

@@

\caption[Main effects over item ratios]{Main effects over item ratios}\label{fig:mainD}
\end{figure}

@@

@@

\caption[2-way interactions over item ratios]{2-way interactions over item ratios}\label{fig:22way}
\end{figure}

@@

@@

@@

\caption[vagueness by number interaction over item ratios]{vagueness by number interaction over item ratios}\label{fig:plotInt2}
\end{figure}

@@

@@

\caption[3 way interactions]{3 way interactions}\label{fig:plot3way}
\end{figure}

@@

@@

\caption[Plot vagueness by number by quantity over item ratios]{Plot vagueness by number by quantity over item ratios.}\label{fig:vnitems}
\end{figure}

@@

@@

\caption[4 way interaction]{4 way interaction}\label{fig:4way}
\end{figure}

@@

@@

\caption[4 way interaction split over item discriminability]{4 way interaction split over item discriminability}\label{fig:4waysplit}
\end{figure}

@@

\clearpage
\section{Lmer model}

@@

% latex table generated in R 3.3.1 by xtable 1.8-2 package
% Fri Aug 12 22:28:46 2016
\begin{table}[htbp]
\begingroup\small
\begin{tabular}{rrrr}
  \hline
 & Estimate & Std. Error & t value \\ 
  \hline
(Intercept) & 7.17 & 0.12 & 58.67 \\ 
  c\_Vag & 0.06 & 0.01 & 4.39 \\ 
  c\_Num & -0.43 & 0.08 & -5.77 \\ 
  c\_Qty & -0.07 & 0.02 & -3.45 \\ 
  c\_Ord & 0.02 & 0.01 & 1.33 \\ 
  discriminability & -0.77 & 0.05 & -15.66 \\ 
  s\_Trl & -0.11 & 0.01 & -18.42 \\ 
  RTprev\_log & 0.06 & 0.01 & 6.24 \\ 
  nchar\_instr & 0.01 & 0.00 & 3.13 \\ 
  c\_Vag:c\_Num:c\_Qty & 0.10 & 0.05 & 2.28 \\ 
   \hline
\end{tabular}
\endgroup
\caption{xtable v5} 
\end{table}

@@

@@

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{v6} \hlkwb{<-} \hlstd{lmerTest}\hlopt{::}\hlkwd{lmer}\hlstd{(}\hlkwc{data} \hlstd{= dd, RT_log} \hlopt{~} \hlstd{c_Vag} \hlopt{+} \hlstd{c_Num} \hlopt{+} \hlstd{c_Qty} \hlopt{+} \hlstd{c_Ord} \hlopt{+} \hlstd{c_Num}\hlopt{:}\hlstd{c_Vag}\hlopt{:}\hlstd{c_Qty} \hlopt{+} \hlstd{discriminability} \hlopt{+}
    \hlstd{s_Trl} \hlopt{+} \hlstd{RTprev_log} \hlopt{+} \hlstd{nchar_instr} \hlopt{+} \hlstd{(}\hlnum{1} \hlopt{+} \hlstd{c_Vag} \hlopt{+} \hlstd{c_Num} \hlopt{+} \hlstd{c_Qty} \hlopt{+} \hlstd{c_Ord} \hlopt{|} \hlstd{Subject))}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

@@

% latex table generated in R 3.3.1 by xtable 1.8-2 package
% Fri Aug 12 22:28:47 2016
\begin{table}[htbp]
\centering
\begingroup\small
\begin{tabular}{rrr}
  \hline
 & Crisp & Vague \\ 
  \hline
expected & 3332 & 2776 \\ 
  borderline & 433 & 841 \\ 
  extreme &  75 & 220 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Borderline cases counts} 
\end{table}

>>>>

\documentclass[a4paper,12pt,twoside]{article}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

@@

\usepackage{alltt}
\usepackage[margin=2cm]{geometry}
\usepackage{placeins}
\usepackage{graphicx}
\usepackage{color}
\usepackage{hyperref}
\title{Exp 2 of 4}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

\clearpage
\subsection{Consider using log RT}

@@

\clearpage
\subsection{How logging RT affects the distribution}

@@

\clearpage
\subsection{Identify fast and slow subjects and items}

@@

\clearpage
\subsection{Plot main effects in both transformations}

@@

{\centering \includegraphics[width=\maxwidth]{figure/graphics-plotMainEffectsRaw-1}

@@

\caption[Plot main effects in raw RT]{Plot main effects in raw RT}\label{fig:plotMainEffectsRaw}
\end{figure}

@@

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[htbp]

{\centering \includegraphics[width=\maxwidth]{figure/graphics-plotMainEffectsLog-1}

@@

\caption[Plot main effects in log RT]{Plot main effects in log RT}\label{fig:plotMainEffectsLog}
\end{figure}

@@

\clearpage
\subsection{Main effects in log RT over discriminability}

@@

\caption[Main effects in log RT over discriminability]{Main effects in log RT over discriminability}\label{fig:mainD}
\end{figure}

@@

\clearpage
\subsection{2-Way interactions over discriminability}

@@

\caption[2-way interactions over discriminability]{2-way interactions over discriminability}\label{fig:22way}
\end{figure}

@@

\clearpage
\subsection{Vagueness by number interaction over items}

@@

\clearpage
\subsection{Vagueness by number interaction over discriminability}

@@

\caption[vagueness by number interaction over discriminability]{vagueness by number interaction over discriminability}\label{fig:plotInt2}
\end{figure}

@@

\clearpage
\subsection{3-Way interactions}

@@

\caption[3-Way interactions]{3-Way interactions}\label{fig:plot3way}
\end{figure}

@@

\clearpage
\subsection{Vagueness by number by quantity over discriminability}

@@

\caption[Vagueness by number by quantity over discriminability]{Vagueness by number by quantity over discriminability}\label{fig:vnitems}
\end{figure}

@@

\clearpage
\subsection{4-Way interaction}

@@

\caption[4-Way interaction]{4-Way interaction}\label{fig:4way}
\end{figure}

@@

\clearpage
\subsection{4-Way interaction split over discriminability}

@@

\caption[4-Way interaction split over discriminability]{4-Way interaction split over discriminability}\label{fig:4waysplit}
\end{figure}

@@

\clearpage
\section{Lmer model: before outlier removal}

@@

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
Linear mixed model fit by REML ['lmerMod']
Formula: RT_log ~ c_Vag + c_Num + c_Qty + c_Ord + c_Num:c_Vag:c_Qty +  
    discriminability + s_Trl + RTprev_log + nchar_instr + (1 +  
    c_Vag + c_Num + c_Qty + c_Ord | Subject)
   Data: dd

Fixed effects:
                   Estimate Std. Error t value
(Intercept)        7.171685   0.122236   58.67
c_Vag              0.060938   0.013873    4.39
c_Num             -0.433614   0.075148   -5.77
c_Qty             -0.069067   0.020047   -3.45
c_Ord              0.017959   0.013497    1.33
discriminability  -0.771402   0.049267  -15.66
s_Trl             -0.106972   0.005807  -18.42
RTprev_log         0.060469   0.009692    6.24
nchar_instr        0.006086   0.001944    3.13
c_Vag:c_Num:c_Qty  0.104949   0.046066    2.28

% latex table generated in R 3.3.1 by xtable 1.8-2 package
% Sat Aug 13 09:11:20 2016
\begin{table}[htbp]
\centering
\begingroup\small
\begin{tabular}{rrrr}
  \hline
 & Estimate & Std. Error & t value \\ 
  \hline
(Intercept) & 7.17 & 0.12 & 58.67 \\ 
  c\_Vag & 0.06 & 0.01 & 4.39 \\ 
  c\_Num & -0.43 & 0.08 & -5.77 \\ 
  c\_Qty & -0.07 & 0.02 & -3.45 \\ 
  c\_Ord & 0.02 & 0.01 & 1.33 \\ 
  discriminability & -0.77 & 0.05 & -15.66 \\ 
  s\_Trl & -0.11 & 0.01 & -18.42 \\ 
  RTprev\_log & 0.06 & 0.01 & 6.24 \\ 
  nchar\_instr & 0.01 & 0.00 & 3.13 \\ 
  c\_Vag:c\_Num:c\_Qty & 0.10 & 0.05 & 2.28 \\ 
   \hline
\end{tabular}
\endgroup
\caption{xtable v5} 
\end{table}

@@

%\clearpage

@@

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{v6} \hlkwb{<-} \hlstd{lmerTest}\hlopt{::}\hlkwd{lmer}\hlstd{(}\hlkwc{data}\hlstd{=dd,}
                     \hlstd{RT_log} \hlopt{~}
                       \hlstd{c_Vag} \hlopt{+} \hlstd{c_Num} \hlopt{+} \hlstd{c_Qty} \hlopt{+} \hlstd{c_Ord} \hlopt{+}
                       \hlstd{c_Num}\hlopt{:}\hlstd{c_Vag}\hlopt{:}\hlstd{c_Qty} \hlopt{+}
                       \hlstd{discriminability} \hlopt{+}
                       \hlstd{s_Trl} \hlopt{+}
                       \hlstd{RTprev_log} \hlopt{+}
                       \hlstd{nchar_instr} \hlopt{+}
                       \hlstd{(}\hlnum{1}\hlopt{+}\hlstd{c_Vag} \hlopt{+} \hlstd{c_Num} \hlopt{+} \hlstd{c_Qty} \hlopt{+} \hlstd{c_Ord}\hlopt{|}\hlstd{Subject))}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\clearpage
\section{Lmer model: after outlier removal}

@@

% latex table generated in R 3.3.1 by xtable 1.8-2 package
% Sat Aug 13 09:11:21 2016
\begin{table}[htbp]
\centering
\begingroup\small
\begin{tabular}{rrr}
  \hline
 & Crisp & Vague \\ 
  \hline
expected & 3332 & 2776 \\ 
  borderline & 433 & 841 \\ 
  extreme &  75 & 220 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Borderline cases counts} 
\end{table}

\clearpage
\appendix
\section{Functions listing}
\clearpage
\subsection{Gather Data}

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{gatherData} \hlkwb{<-} \hlkwa{function}\hlstd{(}\hlkwc{number_of_valid_subjects}\hlstd{) \{}
    \hlstd{data_dir} \hlkwb{<-} \hlstr{"../experimentCode/output/"}
    \hlstd{column.headers.df} \hlkwb{<-} \hlkwd{head}\hlstd{(}\hlkwd{read.table}\hlstd{(}\hlkwd{paste}\hlstd{(data_dir,} \hlstr{"subject01.data"}\hlstd{,} \hlkwc{sep} \hlstd{=} \hlstr{""}\hlstd{),} \hlkwc{header} \hlstd{=} \hlnum{TRUE}\hlstd{),}
        \hlnum{0}\hlstd{)}
    \hlstd{gathered.data} \hlkwb{<-} \hlstd{column.headers.df}
    \hlkwa{for} \hlstd{(subject} \hlkwa{in} \hlnum{1}\hlopt{:}\hlstd{number_of_valid_subjects) \{}
        \hlstd{current.filename} \hlkwb{<-} \hlkwd{paste}\hlstd{(data_dir,} \hlstr{"subject"}\hlstd{,} \hlkwd{sprintf}\hlstd{(}\hlstr{"%02d"}\hlstd{, subject),} \hlstr{".data"}\hlstd{,} \hlkwc{sep} \hlstd{=} \hlstr{""}\hlstd{)}
        \hlstd{current.data} \hlkwb{<-} \hlkwd{read.table}\hlstd{(}\hlkwc{file} \hlstd{= current.filename,} \hlkwc{header} \hlstd{=} \hlnum{TRUE}\hlstd{,} \hlkwc{stringsAsFactors} \hlstd{=} \hlnum{FALSE}\hlstd{)}
        \hlstd{gathered.data} \hlkwb{<-} \hlkwd{rbind}\hlstd{(gathered.data, current.data)}
    \hlstd{\}}
    \hlkwd{message}\hlstd{(}\hlstr{"Returning gathered data"}\hlstd{)}
    \hlkwd{return}\hlstd{(gathered.data)}
\hlstd{\}}  \hlcom{# end of gatherData function}
\end{alltt}
\end{kframe}
\end{knitrout}

\clearpage
\subsection{Classify Response}

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{classifyResponses} \hlkwb{<-} \hlkwa{function}\hlstd{(}\hlkwc{dat}\hlstd{) \{}
    \hlcom{# what were they expected to respond?}
    \hlstd{dat}\hlopt{$}\hlstd{crossed} \hlkwb{<-} \hlkwd{as.factor}\hlstd{(}\hlkwd{paste}\hlstd{(}\hlstr{"Con"}\hlstd{, dat}\hlopt{$}\hlstd{Condition,} \hlstr{":Quan"}\hlstd{, dat}\hlopt{$}\hlstd{Quantity,} \hlstr{":Item"}\hlstd{, dat}\hlopt{$}\hlstd{Item,} \hlkwc{sep} \hlstd{=} \hlstr{""}\hlstd{))}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con1:Quan1:Item1"}\hlstd{,} \hlstr{"Exp_Num"}\hlstd{]} \hlkwb{<-} \hlnum{6}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con1:Quan1:Item1"}\hlstd{,} \hlstr{"Bline_Num"}\hlstd{]} \hlkwb{<-} \hlnum{15}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con1:Quan1:Item1"}\hlstd{,} \hlstr{"Extr_Num"}\hlstd{]} \hlkwb{<-} \hlnum{24}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con1:Quan1:Item2"}\hlstd{,} \hlstr{"Exp_Num"}\hlstd{]} \hlkwb{<-} \hlnum{16}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con1:Quan1:Item2"}\hlstd{,} \hlstr{"Bline_Num"}\hlstd{]} \hlkwb{<-} \hlnum{25}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con1:Quan1:Item2"}\hlstd{,} \hlstr{"Extr_Num"}\hlstd{]} \hlkwb{<-} \hlnum{34}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con1:Quan1:Item3"}\hlstd{,} \hlstr{"Exp_Num"}\hlstd{]} \hlkwb{<-} \hlnum{26}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con1:Quan1:Item3"}\hlstd{,} \hlstr{"Bline_Num"}\hlstd{]} \hlkwb{<-} \hlnum{35}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con1:Quan1:Item3"}\hlstd{,} \hlstr{"Extr_Num"}\hlstd{]} \hlkwb{<-} \hlnum{44}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con1:Quan1:Item4"}\hlstd{,} \hlstr{"Exp_Num"}\hlstd{]} \hlkwb{<-} \hlnum{36}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con1:Quan1:Item4"}\hlstd{,} \hlstr{"Bline_Num"}\hlstd{]} \hlkwb{<-} \hlnum{45}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con1:Quan1:Item4"}\hlstd{,} \hlstr{"Extr_Num"}\hlstd{]} \hlkwb{<-} \hlnum{54}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con1:Quan2:Item1"}\hlstd{,} \hlstr{"Exp_Num"}\hlstd{]} \hlkwb{<-} \hlnum{24}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con1:Quan2:Item1"}\hlstd{,} \hlstr{"Bline_Num"}\hlstd{]} \hlkwb{<-} \hlnum{15}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con1:Quan2:Item1"}\hlstd{,} \hlstr{"Extr_Num"}\hlstd{]} \hlkwb{<-} \hlnum{6}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con1:Quan2:Item2"}\hlstd{,} \hlstr{"Exp_Num"}\hlstd{]} \hlkwb{<-} \hlnum{34}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con1:Quan2:Item2"}\hlstd{,} \hlstr{"Bline_Num"}\hlstd{]} \hlkwb{<-} \hlnum{25}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con1:Quan2:Item2"}\hlstd{,} \hlstr{"Extr_Num"}\hlstd{]} \hlkwb{<-} \hlnum{16}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con1:Quan2:Item3"}\hlstd{,} \hlstr{"Exp_Num"}\hlstd{]} \hlkwb{<-} \hlnum{44}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con1:Quan2:Item3"}\hlstd{,} \hlstr{"Bline_Num"}\hlstd{]} \hlkwb{<-} \hlnum{35}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con1:Quan2:Item3"}\hlstd{,} \hlstr{"Extr_Num"}\hlstd{]} \hlkwb{<-} \hlnum{26}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con1:Quan2:Item4"}\hlstd{,} \hlstr{"Exp_Num"}\hlstd{]} \hlkwb{<-} \hlnum{54}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con1:Quan2:Item4"}\hlstd{,} \hlstr{"Bline_Num"}\hlstd{]} \hlkwb{<-} \hlnum{45}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con1:Quan2:Item4"}\hlstd{,} \hlstr{"Extr_Num"}\hlstd{]} \hlkwb{<-} \hlnum{36}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con2:Quan1:Item1"}\hlstd{,} \hlstr{"Exp_Num"}\hlstd{]} \hlkwb{<-} \hlnum{6}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con2:Quan1:Item1"}\hlstd{,} \hlstr{"Bline_Num"}\hlstd{]} \hlkwb{<-} \hlnum{15}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con2:Quan1:Item1"}\hlstd{,} \hlstr{"Extr_Num"}\hlstd{]} \hlkwb{<-} \hlnum{24}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con2:Quan1:Item2"}\hlstd{,} \hlstr{"Exp_Num"}\hlstd{]} \hlkwb{<-} \hlnum{16}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con2:Quan1:Item2"}\hlstd{,} \hlstr{"Bline_Num"}\hlstd{]} \hlkwb{<-} \hlnum{25}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con2:Quan1:Item2"}\hlstd{,} \hlstr{"Extr_Num"}\hlstd{]} \hlkwb{<-} \hlnum{34}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con2:Quan1:Item3"}\hlstd{,} \hlstr{"Exp_Num"}\hlstd{]} \hlkwb{<-} \hlnum{26}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con2:Quan1:Item3"}\hlstd{,} \hlstr{"Bline_Num"}\hlstd{]} \hlkwb{<-} \hlnum{35}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con2:Quan1:Item3"}\hlstd{,} \hlstr{"Extr_Num"}\hlstd{]} \hlkwb{<-} \hlnum{44}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con2:Quan1:Item4"}\hlstd{,} \hlstr{"Exp_Num"}\hlstd{]} \hlkwb{<-} \hlnum{36}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con2:Quan1:Item4"}\hlstd{,} \hlstr{"Bline_Num"}\hlstd{]} \hlkwb{<-} \hlnum{45}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con2:Quan1:Item4"}\hlstd{,} \hlstr{"Extr_Num"}\hlstd{]} \hlkwb{<-} \hlnum{54}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con2:Quan2:Item1"}\hlstd{,} \hlstr{"Exp_Num"}\hlstd{]} \hlkwb{<-} \hlnum{24}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con2:Quan2:Item1"}\hlstd{,} \hlstr{"Bline_Num"}\hlstd{]} \hlkwb{<-} \hlnum{15}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con2:Quan2:Item1"}\hlstd{,} \hlstr{"Extr_Num"}\hlstd{]} \hlkwb{<-} \hlnum{6}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con2:Quan2:Item2"}\hlstd{,} \hlstr{"Exp_Num"}\hlstd{]} \hlkwb{<-} \hlnum{34}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con2:Quan2:Item2"}\hlstd{,} \hlstr{"Bline_Num"}\hlstd{]} \hlkwb{<-} \hlnum{25}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con2:Quan2:Item2"}\hlstd{,} \hlstr{"Extr_Num"}\hlstd{]} \hlkwb{<-} \hlnum{16}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con2:Quan2:Item3"}\hlstd{,} \hlstr{"Exp_Num"}\hlstd{]} \hlkwb{<-} \hlnum{44}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con2:Quan2:Item3"}\hlstd{,} \hlstr{"Bline_Num"}\hlstd{]} \hlkwb{<-} \hlnum{35}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con2:Quan2:Item3"}\hlstd{,} \hlstr{"Extr_Num"}\hlstd{]} \hlkwb{<-} \hlnum{26}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con2:Quan2:Item4"}\hlstd{,} \hlstr{"Exp_Num"}\hlstd{]} \hlkwb{<-} \hlnum{54}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con2:Quan2:Item4"}\hlstd{,} \hlstr{"Bline_Num"}\hlstd{]} \hlkwb{<-} \hlnum{45}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con2:Quan2:Item4"}\hlstd{,} \hlstr{"Extr_Num"}\hlstd{]} \hlkwb{<-} \hlnum{36}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con3:Quan1:Item1"}\hlstd{,} \hlstr{"Exp_Num"}\hlstd{]} \hlkwb{<-} \hlnum{6}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con3:Quan1:Item1"}\hlstd{,} \hlstr{"Bline_Num"}\hlstd{]} \hlkwb{<-} \hlnum{15}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con3:Quan1:Item1"}\hlstd{,} \hlstr{"Extr_Num"}\hlstd{]} \hlkwb{<-} \hlnum{24}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con3:Quan1:Item2"}\hlstd{,} \hlstr{"Exp_Num"}\hlstd{]} \hlkwb{<-} \hlnum{16}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con3:Quan1:Item2"}\hlstd{,} \hlstr{"Bline_Num"}\hlstd{]} \hlkwb{<-} \hlnum{25}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con3:Quan1:Item2"}\hlstd{,} \hlstr{"Extr_Num"}\hlstd{]} \hlkwb{<-} \hlnum{34}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con3:Quan1:Item3"}\hlstd{,} \hlstr{"Exp_Num"}\hlstd{]} \hlkwb{<-} \hlnum{26}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con3:Quan1:Item3"}\hlstd{,} \hlstr{"Bline_Num"}\hlstd{]} \hlkwb{<-} \hlnum{35}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con3:Quan1:Item3"}\hlstd{,} \hlstr{"Extr_Num"}\hlstd{]} \hlkwb{<-} \hlnum{44}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con3:Quan1:Item4"}\hlstd{,} \hlstr{"Exp_Num"}\hlstd{]} \hlkwb{<-} \hlnum{36}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con3:Quan1:Item4"}\hlstd{,} \hlstr{"Bline_Num"}\hlstd{]} \hlkwb{<-} \hlnum{45}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con3:Quan1:Item4"}\hlstd{,} \hlstr{"Extr_Num"}\hlstd{]} \hlkwb{<-} \hlnum{54}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con3:Quan2:Item1"}\hlstd{,} \hlstr{"Exp_Num"}\hlstd{]} \hlkwb{<-} \hlnum{24}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con3:Quan2:Item1"}\hlstd{,} \hlstr{"Bline_Num"}\hlstd{]} \hlkwb{<-} \hlnum{15}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con3:Quan2:Item1"}\hlstd{,} \hlstr{"Extr_Num"}\hlstd{]} \hlkwb{<-} \hlnum{6}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con3:Quan2:Item2"}\hlstd{,} \hlstr{"Exp_Num"}\hlstd{]} \hlkwb{<-} \hlnum{34}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con3:Quan2:Item2"}\hlstd{,} \hlstr{"Bline_Num"}\hlstd{]} \hlkwb{<-} \hlnum{25}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con3:Quan2:Item2"}\hlstd{,} \hlstr{"Extr_Num"}\hlstd{]} \hlkwb{<-} \hlnum{16}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con3:Quan2:Item3"}\hlstd{,} \hlstr{"Exp_Num"}\hlstd{]} \hlkwb{<-} \hlnum{44}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con3:Quan2:Item3"}\hlstd{,} \hlstr{"Bline_Num"}\hlstd{]} \hlkwb{<-} \hlnum{35}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con3:Quan2:Item3"}\hlstd{,} \hlstr{"Extr_Num"}\hlstd{]} \hlkwb{<-} \hlnum{26}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con3:Quan2:Item4"}\hlstd{,} \hlstr{"Exp_Num"}\hlstd{]} \hlkwb{<-} \hlnum{54}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con3:Quan2:Item4"}\hlstd{,} \hlstr{"Bline_Num"}\hlstd{]} \hlkwb{<-} \hlnum{45}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con3:Quan2:Item4"}\hlstd{,} \hlstr{"Extr_Num"}\hlstd{]} \hlkwb{<-} \hlnum{36}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con4:Quan1:Item1"}\hlstd{,} \hlstr{"Exp_Num"}\hlstd{]} \hlkwb{<-} \hlnum{6}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con4:Quan1:Item1"}\hlstd{,} \hlstr{"Bline_Num"}\hlstd{]} \hlkwb{<-} \hlnum{15}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con4:Quan1:Item1"}\hlstd{,} \hlstr{"Extr_Num"}\hlstd{]} \hlkwb{<-} \hlnum{24}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con4:Quan1:Item2"}\hlstd{,} \hlstr{"Exp_Num"}\hlstd{]} \hlkwb{<-} \hlnum{16}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con4:Quan1:Item2"}\hlstd{,} \hlstr{"Bline_Num"}\hlstd{]} \hlkwb{<-} \hlnum{25}
    \hlstd{dat[dat}\hlopt{$}\hlstd{crossed} \hlopt{==} \hlstr{"Con4:Quan1:Item2"}\hlstd{,} \hlstr{"Extr_Num"}\hlstd{]} \hlkwb{<-} \hlnum{34}
